---
title: Task 3 Coding Test
author: "Milad Naeimi"
date: "2023-05-15"
output: pdf_document
---

####Task 3
#Step 1: Network overlap: with the "following.json" dataset, write a function that takes any two influencers' user ID's and calculate the fraction of followers these two influencers share over the total number of followers of the less followed influencer. The reference date is April 30, 2022.	

####Setting the root File
```{r}
setwd("C:/Users/milad/OneDrive/Desktop/Jobs/Coding Tasks/task3")
getwd()
```

```{r}
library(dplyr)
library(stringr)
library(jsonlite)
library(dplyr)
#install.packages("anytime")
library(anytime)
#install.packages("lubridate")
library(lubridate)
calculate_network_overlap <- function(user1_id, user2_id) {
  # Load the "following.json" dataset
  following_data <- fromJSON("following.json")
# Extract the date from the time string using regular expressions
  following_data$follow_timestamp <- gsub("\\..*$", "", following_data$follow_timestamp)  # Remove milliseconds
  following_data$follow_timestamp <- gsub("T", " ", following_data$follow_timestamp)  # Replace 'T' with space
  following_data$follow_timestamp <- as.Date(following_data$follow_timestamp)

  # Filter data for the reference date (April 30, 2022)
  reference_date <- as.Date("2022-04-30")
  following_data <- following_data %>% filter(follow_timestamp <= reference_date)

  # Get the number of followers for user1 and user2
  user1_followers <- following_data %>% filter(influencer_uid == user1_id) %>% distinct(follower_uid)
  user2_followers <- following_data %>% filter(influencer_uid == user2_id) %>% distinct(follower_uid)

  # Count the number of followers for user1 and user2
  user1_followers_count <- nrow(user1_followers)
  user2_followers_count <- nrow(user2_followers)

  # Calculate the fraction of followers shared by the two influencers
  overlap_fraction <- nrow(intersect(user1_followers, user2_followers)) / min(user1_followers_count, user2_followers_count)

  return(overlap_fraction)
}

# Example usage
influencer1_id <- "902200087"  
influencer2_id <- "14709326"  

overlap_fraction <- calculate_network_overlap(influencer1_id, influencer2_id)
print(overlap_fraction)

```



#Step 2: Engagement overlap: with the "engagement.json" dataset, write a function that takes any two influencers' user ID's and calculate the fraction of engagers of these two influencers' tweets as a function of the total number of engagers of the less engaged influencer, over the period of April 22, 2022 to April 30, 2022.										
```{r}
library(jsonlite)
library(dplyr)
calculate_engagement_overlap <- function(user_id1, user_id2) {
  # Load the engagement data from "engagement.json"
  data <- jsonlite::read_json("engagement.json")
  
  # Extract the date from the time string using regular expressions
  data$follow_timestamp <- gsub("\\..*$", "", data$follow_timestamp)  # Remove milliseconds
  data$follow_timestamp <- gsub("T", " ", data$follow_timestamp)  # Replace 'T' with space
  data$follow_timestamp <- as.Date(data$follow_timestamp)

  # Filter the data for the specified time period (April 22, 2022, to April 30, 2022)
reference_date1 <- as.Date("2022-04-22")
reference_date2 <- as.Date("2022-04-30")

filtered_data <- data %>% 
  filter(follow_timestamp >= reference_date1 & follow_timestamp <= reference_date2)
  # Filter the data for the specified time period (April 22, 2022, to April 30, 2022)
  filtered_data <- data[data$follow_timestamp >= 1650624000 & data$follow_timestamp <= 1651382399, ]
  
  # Find the tweets of the two influencers
  influencer1_tweets <- filtered_data[filtered_data$influencer_uid == user_id1, ]
  influencer2_tweets <- filtered_data[filtered_data$influencer_uid == user_id2, ]
  
  # Calculate the number of engagers for each influencer
  influencer1_engagers <- unique(unlist(influencer1_tweets$follower_uid))
  influencer2_engagers <- unique(unlist(influencer2_tweets$follower_uid))
  
  # Calculate the fraction of engagers of the less engaged influencer
  num_engagers_less_engaged <- min(length(influencer1_engagers), length(influencer2_engagers))
  
  if (num_engagers_less_engaged == 0) {
    return(0)
  }
  
  fraction_overlap <- length(intersect(influencer1_engagers, influencer2_engagers)) / num_engagers_less_engaged
  
  return(fraction_overlap)
}

# Example usage
user_id1 <- "902200087"
user_id2 <- "14709326"
engagement_overlap <- calculate_engagement_overlap(user_id1, user_id2)
cat(paste("Engagement overlap fraction between", user_id1, "and", user_id2, ":", overlap_fraction))

```
#Step 3: Produce two histograms of network overlap (Step 2) and engagement overlap (Step 3) measures, respectively, across all influencer pairs										
```{r}
# Create a new plotting window
dev.new()

# Plot histogram for network overlap
hist(overlap_fraction, main = "Network Overlap", xlab = "Overlap", col = "blue")

# Create a new plotting window
dev.new()

# Plot histogram for engagement overlap
hist(overlap_fraction_engagement, main = "Engagement Overlap", xlab = "Overlap", col = "green")
```


#Step 5: Use OLS to regress engagement overlap on network overlap measures for all influencers pairs, and plot the regression results on a two-dimensional graph with standard error bands.										
```{r}
# Create a data frame with the variables
dataset <- data.frame(network_overlap, engagement_overlap)

# Perform OLS regression
model <- lm(engagement_overlap ~ network_overlap, data = data)

# Calculate predicted values and standard errors
predicted <- predict(model)
se <- sqrt(diag(vcov(model)))

# Plot regression results with standard error bands
plot(network_overlap, engagement_overlap, pch = 16, xlab = "Network Overlap", ylab = "Engagement Overlap", main = "Regression of Engagement Overlap on Network Overlap")
abline(model, col = "blue")  # Regression line
lines(network_overlap, predicted, col = "red")  # Predicted values
lines(network_overlap, predicted + 2*se, col = "green", lty = "dashed")  # Upper bound (2 standard errors)
lines(network_overlap, predicted - 2*se, col = "green", lty = "dashed")  # Lower bound (2 standard errors)
legend("topleft", legend = c("Regression Line", "Predicted Values", "Standard Error Bands"), col = c("blue", "red", "green"), lty = c(1, 1, "dashed"))
```





















